Multi-product Batch Processing Time Maximization Problem

### 2023-07-04 (2023) Fraga et al.tex
updating paper

\documentclass[preprint,12pt,authoryear]{elsarticle}

@@

\title{Multiproduct Batch Processing Time Maximization Problem}

@@

\author{Tatiana Balbi Fraga and Regilda da Costa e Silva Menêzes}

@@

The scientific literature presents several papers that address multi-product batch problens. Many works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine the production sequence of the products and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}. In this problem, a single product is processed at a time, so it is necessary that the quantity produced is sufficient to meet the demand during the period in which other products are being processed. The solution must be determined in such a way that both setup and storage costs are minimized. Among the authors who addressed this problem are \cite{Eilon1985}, \cite{Omega1993} and \cite{LiuEtAl2020}. In the papers mentioned above, production in a single unit or in a serial flowshop plant is considered, in which all products follow the same linear flow through the production units. \cite{KimEtAl1996} consider the multi-product batch problem in networked processes. As defined by the authors, in this case, the production units are not arranged in a line, and the connection between the units may or may not exist. Therefore, the production paths in the flowshop network can be different for each product. Also the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence. Other important works deal with the problem of a multi-product batch plant design (MPBPD). In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements \citep{RavemarkAndRippin1998}.

@@

$\textrm{UD}_i$ is the demand for the product $i$; \\

$\textrm{I}$ is the maximum quantity allowed for additional factory storage of all products in the batch; \\

$\textrm{UI}_i$ is the maximum quantity allowed for stocking the product $i$ in the factory; \\

$\textrm{O}$ is the maximum quantity allowed for shipment of all products to outlets; \\

$\textrm{UO}_i$ is the maximum amount of product $i$ that can be shipped to outlets; \\

$\textrm{p}_i$ is the production rate of product $i$; \\

$\textrm{Z}$ is the timeout for batch processing; \\

$P_i$ is the amount of product $i$ produced; \\

$D_i$ is the amount of product $i$ delivered for the demand; \\

$O_i$ amount of product $i$ shipped to factory outlets; \\

$I_i$ is the amount of product $i$ that will be stored at the factory; \\

@@

@@

@@

So the solution method can be decomposed into 4 steps: \\

step 1: find $T'$, where:

\begin{equation}
T' = \lfloor{\min_{\forall i} \{\textrm{UD}_i / \textrm{p}_i\}}\rfloor
\end{equation}

step 2: calculate $S_i$ for all products.

\begin{equation}
\label{eq:unmet}
S_i = \textrm{UD}_i - \textrm{p}_i * T' \quad \forall i
\end{equation}

step 3: find $T''$, where:

\begin{equation}
T'' = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}}\rfloor
\end{equation}

step 4: calculate $T$, where:

\begin{equation}
T = \min \{T , \textrm{Z}\}
\end{equation}

@@

Note that it is not important to know the values of $O_i$ and $I_i$ $\forall i$ however these values can be found by taking a solution from the indeterminate system of inequations:

@@

Table \ref{tab:results} presents the results obtained by applying the analytical method (C++ solver) and the LINGO solver for the solution of the previously presented benchmarks.

\begin{table}[h]
\begin{center}
\begin{footnotesize}
\begin{tabular}[c]{l r r r r}
problem & LINGO solver & time (s) & analytical method & time (s) \\
\cline {1-5} \\
MBPTMP 1 & 55 & 0 & 55 & 0.001 \\
MBPTMP 2 & 48 & 0.06 & 48 & 0.001 \\
MBPTMP 3 & & & 30 & 0.001 \\
RMBPTMP 20 & & & 100 & 0.001 \\
RMBPTMP 50 & & & 98 & 0.001\\
RMBPTMP 100 & & & 98 & 0.002\\
RMBPTMP 1,000 & & & 78 & 0.002\\
RMBPTMP 10,000 & & & 70 & 0.006 \\
\cline {1-5} \\
\end{tabular}
\label{tab:results}
\caption{Results obtained with the LINGO solver and the analytical method}
\end{footnotesize}
\end{center}
\end{table}

\section{Contributions}
\label{sec:contributions}

The work for the elaboration of this paper is being carried out by two professors, as described below. Professor Fraga, T.B., was responsible for identifying the problem, mathematical modeling, proposing an analytical solution, developing a solver in C ++ for the analytical solution and a solver in LINGO for validating the mathematical model, developing benchmarks, and testing the analytical method and the solver in C++, as well as surveying bibliography and elaboration of the paper. Professor Menezes, R. D. C. S. is contributing to the bibliographic survey.

>>>>

\documentclass[authoryear,preprint,12pt]{elsarticle}

%% The `ecrc' package must be called to make the CRC functionality available
%\usepackage{ecrc}

@@

\title{Multi-product Batch Processing Time Maximization Problem}

@@

\author{Tatiana Balbi Fraga, Ítalo Ruan Barbosa de Aquino and Regilda da Costa e Silva Menêzes}

@@

The scientific literature presents several papers that address multi-product batch problems. Many works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine the production sequence of the products and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}. In this problem, a single product is processed at a time, so it is necessary that the quantity produced is sufficient to meet the demand during the period in which other products are being processed. The solution must be determined in such a way that both setup and storage costs are minimized. Among the authors who addressed this problem are \cite{Eilon1985}, \cite{Omega1993} and \cite{LiuEtAl2020}. In the papers mentioned above, production in a single unit or in a serial flowshop plant is considered, in which all products follow the same linear flow through the production units. \cite{KimEtAl1996} consider the multi-product batch problem in networked processes. As defined by the authors, in this case, the production units are not arranged in a line, and the connection between the units may or may not exist. Therefore, the production paths in the flowshop network can be different for each product. Also the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence. Other important works deal with the problem of a multi-product batch plant design (MPBPD). In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements \citep{RavemarkAndRippin1998}.

@@

$\textrm{UD}_i$ is the demand for the product $i$;

$\textrm{I}$ is the maximum quantity allowed for additional factory storage of all products in the batch;

$\textrm{UI}_i$ is the maximum quantity allowed for stocking the product $i$ in the factory;

$\textrm{O}$ is the maximum quantity allowed for shipment of all products to outlets;

$\textrm{UO}_i$ is the maximum amount of product $i$ that can be shipped to outlets;

$\textrm{p}_i$ is the production rate of product $i$;

$\textrm{Z}$ is the timeout for batch processing;

$P_i$ is the amount of product $i$ produced;

$D_i$ is the amount of product $i$ delivered for the demand;

$O_i$ amount of product $i$ shipped to factory outlets;

$I_i$ is the amount of product $i$ that will be stored at the factory;

@@

$s.t.$

@@

\begin{equation}
T, D_i, O_i, I_i \in  \mathbb{Z}^+ \quad \forall i
\end{equation}

@@

So, the analytical method can be decomposed into 4 steps: \\

step 1: find $T'$, where:
\begin{equation}
T' = \lfloor{\min_{\forall i} \{\textrm{UD}_i / \textrm{p}_i\}}\rfloor
\end{equation}

step 2: calculate $S_i$ for all products.
\begin{equation}
\label{eq:unmet}
S_i = \textrm{UD}_i - \textrm{p}_i * T' \quad \forall i
\end{equation}

step 3: find $T''$, where:
\begin{equation}
T'' = \lfloor{\min \{\min_{\forall i} \{(\textrm{UO}_i + \textrm{UI}_i + S_i) / \textrm{p}_i\},(\textrm{O} + \textrm{I} + \sum_i {S_i}) / \sum_i {\textrm{p}_i}\}}\rfloor
\end{equation}

step 4: calculate $T$, where: 
\begin{equation}
T = T' + T''
\end{equation}
\begin{equation}
T = \min \{T , \textrm{Z}\}
\end{equation}

@@

Note that it is not important to know the values of $O_i$ and $I_i$, $\forall i$, however, after determining $T$, these values can be found by taking a solution from the model:

\begin{equation}
max \quad \sum_i{D_i}
\end{equation}

$s.t.$

\begin{equation}
P_i  = \textrm{p}_i * T \quad \forall i
\end{equation}

\begin{equation}
D_i - O_i - I_i = P_i \quad \forall i
\end{equation}

@@

Table \ref{tab:results} presents the results obtained by applying the analytical method (C++ solver) and the LINGO solver for the solution of the previously presented benchmarks. \\

\begin{table}[h]
\begin{center}
\begin{footnotesize}
\begin{tabular}[c]{l r r r r}
problem & LINGO solver & time (s) & analytical method & time (s) \\
\cline {1-5} \\
MBPTMP 1 & 55 & 0.04 & 55 & 0.001 \\
MBPTMP 2 & 48 & 0.06 & 48 & 0.001 \\
MBPTMP 3 & 30 & 0.09 & 30 & 0.001 \\
RMBPTMP 20 & 100 & 0.08 & 100 & 0.001 \\
RMBPTMP 50 & 98 & 0.12 & 98 & 0.001\\
RMBPTMP 100 & 98 & 0.12 & 98 & 0.002\\
RMBPTMP 1,000 & 78 & 3.10 & 78 & 0.002\\
RMBPTMP 10,000 & 70 & 168.87 & 70 & 0.006 \\
\cline {1-5} \\
\end{tabular}
\label{tab:results}
\caption{Results obtained with the LINGO solver and the analytical method}
\end{footnotesize}
\end{center}
\end{table}

It is important to point out that the LINGO solver was developed with the purpose of validating the results found by the proposed analytical method. As the analytical method is non-polynomial, we did not intend to compare machine processing times, however it is possible to verify that both solvers are capable of finding optimal solutions for the proposed benchmarks very quickly, even for very large problems.

We have considered here a one-day period problem, so in a future work we will study the complexities of solving a multi period problem and try to propose new solution methods if needed.

\section{Contributions to this work}
\label{sec:contributions}

The work for the elaboration of this paper was carried out by tree contributors, as described below. Aquino, Í.R.B., developed the detailed study on the plastic bag production process, which made it possible to identify the problem addressed in this paper. Professor Fraga, T.B., was responsible for identifying the problem, mathematical modeling, proposing an analytical solution, developing a solver in C ++ for applying the analytical solution and a solver in LINGO for validating the mathematical model and the results found by the first solver, developing benchmarks, and testing the model and analytical method proposed, as well as surveying bibliography and elaboration of the paper. Professor Menezes, R. D. C. S., contributed to the bibliographic survey. The authorship of this work follows as described contributions.

In this paper we presented the Multi-product Batch Processing Time Maximization Problem, as well as a mathematical model and an analytical solution method for this problem. The mathematical model and analytical method were tested, respectively, by a solver developed with the LINGO tool, from LINDO Systems, and with a solver developed in C++ language. Optimum results were found for all proposed benchmarks, very quickly, even in the case of very large problems, which demonstrates the efficiency of the proposed method. As in this paper we considered a planning period of one day, in a future work we will study the complexities that arise when considering the same problem with more than one day of planning. We will also verify if there is the possibility of extending the proposed analytical method to solve a class of linear integer programming problems with similar characteristics to the studied problem.
